Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-07-19 ms.tex
added a few senences on the transit light source effect.

One possible explanation for the planet disintegration is that it is tied to stellar activity.
\citet{kawahara2013starspots} found an anti-correlation between stellar flux and the depth of transit events and suggested that the alignment of the planet's position (true anomaly) with active regions on the star causes disintegration.
The alignment of spots and disintegration activity could be due to XUV photoevaporation or magnetic reconnection events.
The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots} though they find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Thanks to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.

>>>>

One possible explanation for the planet disintegration is that it is tied to stellar activity.
\citet{kawahara2013starspots} found an anti-correlation between stellar flux and the depth of transit events and suggested that the alignment of the planet's position (true anomaly) with active regions on the star causes disintegration.
The alignment of spots and disintegration activity could be due to XUV photoevaporation or magnetic reconnection events.
The anti-correlation between stellar flux and transit depth was confirmed by \citet{croll2015starspots}, though the authors find that occultations of star spots can also modulate the transit depth at the 22.9 day rotation period of the star.
Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths exoplanets of M stars, the ``transit source light effect.''
For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can vary by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin Rackham, private communication, 2018}
The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage.

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Thanks to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
Thanks to Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star.
